The Blue Obelisk five years on

### 2011-03-10 paper.tex
InChI

>>>>

The IUPAC InChI identifier is a non-proprietary and unique identifier for chemical substances designed to enable linking of diverse data compilations. Although its development predates the Blue Obelisk, software such as Open Babel has included InChI support since 2005. Since the official InChI implementation is in C, it is difficult to access from the other widely used language for cheminformatics toolkits, Java. The Blue Obelisk project JNI-InChI has been set up to solve this problem by using the Java Native Interface to link the InChI binary to Java. In this way, it promotes the wider adoption of this standard identifier by the chemistry community.
